---
title: "power analysis"
output: html_document
---

```{r,echo=F}
rm(list=ls())
library(ggplot2)
library(gridExtra)
library(matrixStats)
library(plotROC)
library(grid)
library(tidyverse)
library(cowplot)
```

This is power calculation used in the grant proposal.  

```{r, echo=F}
## to mimic the Alzheimer disease (1) prevalence rate 10% (2) sample size 20,000

```


```{r, echo=F}
# run code FullModelEM_MoreRiskVarCate_VaryGammabar.R 
######################## coding ##############
rm("Ui", "mirage_pvalue", "mirage_BF", "fisher_pvalue", "skato_pvalue")
load("C://Shengtong//Research//mirage-alzheimer//mirage-alzheimer//output//power-calculation//6methods_delta0.1_gammamean335.RData")
i=1
Ui=Gene.Risk.Status[[i]]
mirage_pvalue=MIRAGE.pvalue[[i]]
mirage_BF=MIRAGE.BF[[i]]
fisher_pvalue=Fisher.pvalue[[i]]
skato_pvalue=SKATO.pvalue[[i]]

num_run=length(mirage_pvalue)


method=rep(c("MIRAGE-LRT", "Burden", "SKATO", "MIRAGE-BF"), each=num_run)
#roc_single_run=data.frame(D=Ui, m=c(-log(mirage_pvalue, base=10),-log(fisher_pvalue, base=10), -log(skato_pvalue, base=10)), method=method)
roc_single_run=data.frame(D=Ui, m=c(mirage_pvalue,fisher_pvalue,skato_pvalue, -mirage_BF), method=method)
p1.basic=ggplot(roc_single_run, aes(d = D, m = m, color=method), size=2) + 
  geom_roc(increasing=F, n.cuts=0)+
  style_roc(theme = theme_grey)
#
#p1=p1.basic+
#  annotate("text", x =rep(0.8, 4), y = c(0.02,0.08, 0.14, 0.2), 
#           label = paste(c("Burden:AUC=", "MIRAGE-BF:AUC=", "MIRAGE-LRT:AUC=", "SKATO:AUC="), #round(calc_auc(p1.basic)$AUC, 2)), size=1.5)+
#  ggtitle(expression(paste(delta, "=0.1")))+
#theme(plot.title = element_text(hjust = 0.5, size=10))+  #center the title 
# theme(axis.text.x= element_text(size=6))+  # custmorize the axis tick size 
#theme(axis.text.y= element_text(size=6))+
#  theme(axis.text = element_text(size = 1))
auc=round(calc_auc(p1.basic)$AUC, 2)
coding_auc=tibble(AUC=c(0.45, 0.86), Annotation=c("No", "Yes"))
g1=ggplot(coding_auc, aes(x=Annotation, y=AUC, fill=Annotation)) +
  geom_bar(stat="identity")+
  ylim(c(0,1))+
  xlab("Coding")+
  guides(fill=FALSE)+  # remove legend 
theme_classic()
g1

############################# non-coding #############
rm("Ui", "mirage_pvalue", "mirage_BF", "fisher_pvalue", "skato_pvalue")
load("C://Shengtong//Research//mirage-alzheimer//mirage-alzheimer//output//power-calculation//6methods_delta0.05_gammamean113.RData")
i=1
Ui=Gene.Risk.Status[[i]]
mirage_pvalue=MIRAGE.pvalue[[i]]
mirage_BF=MIRAGE.BF[[i]]
fisher_pvalue=Fisher.pvalue[[i]]
skato_pvalue=SKATO.pvalue[[i]]

num_run=length(mirage_pvalue)


method=rep(c("MIRAGE-LRT", "Burden", "SKATO", "MIRAGE-BF"), each=num_run)
#roc_single_run=data.frame(D=Ui, m=c(-log(mirage_pvalue, base=10),-log(fisher_pvalue, base=10), -log(skato_pvalue, base=10)), method=method)
roc_single_run=data.frame(D=Ui, m=c(mirage_pvalue,fisher_pvalue,skato_pvalue, -mirage_BF), method=method)
p1.basic=ggplot(roc_single_run, aes(d = D, m = m, color=method), size=2) + 
  geom_roc(increasing=F, n.cuts=0)+
  style_roc(theme = theme_grey)
#
#p1=p1.basic+
#  annotate("text", x =rep(0.8, 4), y = c(0.02,0.08, 0.14, 0.2), 
#           label = paste(c("Burden:AUC=", "MIRAGE-BF:AUC=", "MIRAGE-LRT:AUC=", "SKATO:AUC="), #round(calc_auc(p1.basic)$AUC, 2)), size=1.5)+
#  ggtitle(expression(paste(delta, "=0.1")))+
#theme(plot.title = element_text(hjust = 0.5, size=10))+  #center the title 
# theme(axis.text.x= element_text(size=6))+  # custmorize the axis tick size 
#theme(axis.text.y= element_text(size=6))+
#  theme(axis.text = element_text(size = 1))
auc=round(calc_auc(p1.basic)$AUC, 2)
noncoding_auc=tibble(AUC=c(0.46, 0.78), Annotation=c("No", "Yes"))
g2=ggplot(noncoding_auc, aes(x=Annotation, y=AUC, fill=Annotation)) +
  geom_bar(stat="identity")+
  ylim(c(0,1))+
  xlab("Noncoding")+ylab("")+
theme_classic()
g2

grid.arrange(g1, g2,  nrow=1)

```

Coding: sample size, $N1=N0=20,000$; 100 genes (regions) and $10\%$ are risk genes; each risk gene has 100 variants in 3 variant groups, $60\%$ are in the first group with RR $\bar{\gamma}=3$ and the risk variants proportion is  $\eta_1=5\%$, $30\%$ in the second group with $\bar{\gamma}=3$ with $\eta_2=20\%$ and the last $10\%$ has $\bar{\gamma}=5$ with $\eta_3=50\%$. 

Noncoding:  sample size, $N1=N0=20,000$; 100 regions and $5\%$ are risk regions; each risk region has 100 variants in 3 variant groups, $60\%$ are in the first group with RR $\bar{\gamma}=1$ and the risk variants proportion is  $\eta_1=5\%$, $30\%$ in the second group with $\bar{\gamma}=1$ with $\eta_2=20\%$ and the last $10\%$ has $\bar{\gamma}=3$ with $\eta_3=50\%$.


Annotation: "Yes" represents using mirage with annotations and "No" is for burden test without annotations.  
